Collision rates of planetesimals near mean-motion resonances

### 2020-10-29 refereeResponse.txt

    Be sure to add chapter, page number and eq number after all M+D equations. The main purpose of this section is to explain how we calculated resonances widths that were used in the later parts of the paper. Go back through and make sure each of the equations presented is referenced later in the paper. Remove ones that arent

I am not saying equations are wrong, but please, revise all equations to make sure they are correct and consistent, and add explanation when clarification is needed.

10) Equation (5) - should'n this equation have -q instead of -(2p+q) in the third term and -p instead of -q in the second term? See for example Murray & Dermott (1999, chap 8, eq. 8.8), or Beaugé & Ferraz-Mello (1993), or Malhotra (1993), or Gomes (1995)...
From Murray & Dermott (1999, Chap 6 and 8), one of the general forms of the resonant angle can be phi = j1*lamb' + j2*lamb + j4*varpi, where j1 = p+q, j2 = -p and j4 = -q. So why using j2 = -q and j4 = -(2p+q) instead?
The authors should explicitly say, and explain why these choices were made.

    The argument should indeed by -q, rather than -(2p+q). This mistake was carried through when writing up the equations in the paper, although it appears we properly used j4 = -q when doing our analysis and constructing plots. (2p+q) has been replaced by q in equations 5 and 6 in the paper (also need to fix 14).

@@

19) pg.3 rcol P.2 l.33 - "... 5.2 AU orbit..." - 1) Why not closer distances? 2) AU -> au (here and elsewhere).

    Another sentence was added to the first paragraph of section 3.2 which explains our choice of parameters more clearly. The 'nominal' simulation is meant to be compared directly with simulation B of Richardson et al. 2000, although we reduce the width of the planetesimal annulus to reduce the number of particles required (while still covering all of the promininent interior MMRs). AU has been changed to au everywhere in the paper.

20) pg.3 rcol P.2 l.34 - "The planetesimal disc extends from 2.2 to 3.8 AU..." - Why not consider the outer disk too? External resonances can be very strong and capture is more likely there.

    This is a good point. Our work was mainly motivated by the non-result seen by Richardson et al. 2000, which is why we focus on interior MMRs here. Additionally, the number of timesteps required to measure the collision profile for the exterior MMRs increases with semimajor axis when using alpha steeper than -1. TODO: Add a discussion at the end of the paper explaining that exterior MMRs are interesting too.

@@

21) pg.3 rcol P.2 l.41 - This is a minor comment. I am just curious. Why not using alpha = -1 or -0.9 as it seems more common for protoplanetary disks? -1.5 is an approximation for the Minimum Mass Solar Nebula based on the current solar system planets. Observations of proptoplanetary disks sugggest alpha = -1 or -0.9.

    See 19) and 20). While there is certainly evidence that the gaseous component of the outer regions of protoplanetary disks follow alpha = -1, there is little evidence to suggest that this is the case for solids in the inner planet-forming region. Although alpha = -1.5 is not motivated by any extrasolar observations, it is compatible with the majority of protoplanetary disk models.

@@

22) pg.3 rcol P.2 l.44 - "Each simulation is evolved for 5,000 years" - Could you, please, add discussion regarding simulation time, as well as, define what is a short and long time. For me 5000 yr is, in principle, too short (see my concern #4).

    See our response to concern #4. Some text has been added to the paper to elaborate on this as well.

@@

23) pg.3 rcol P.3 l.44-46 - "The dynamical effects of secular forcing by the giant planet, along with the effects of viscous stirring and gas drag on the planetesimals, are built into the initial conditions." - From the text, It is not clear whether the authors are considering the gas disk phase or not?

    We are considering the gas disk phase here, while making the assumption that the effects of for gas drag on the planetesimals is very weak. In the initial conditions, we tune dynamical excitation of the planetesimals so that the effects of viscous stirring and gas drag (had we imparted a drag force on the particles in the simulation) are in balance. The gravitational stirring time is much longer than 5,000 years, so our planetesimal disk will not suffer from too much dynamical heating because we did not model the gas. More text has been added to this section to explain this more clearly.

@@

26) pg.4 lcol P.2 l.49 - "dynamical timescale of planetesimals..." - What do you mean by dynamical timescale of planetesimals? Collisional timescale, drift timescale, what?

    1/sqrt(G*rho_pl), which sets the timescale for gravitational interactions between planetesimals that undergo close encounters

27) pg.4 rcol P.1 l.41 - "... T_lib ~ 1,000 - 2,000 years..." - So the integration time is about a factor of 2-4 T_lib. Is this enough to take conclusions? Please, see my concern and add discussion.

    In our case, the large particle count allows us to look at the 'ensemble average' of the dynamical behavior near resonance. Even though individual planetesimals only go through a few librational periods, the phase trajectories that they follow are well populated and allow us to make conclusions about the dynamics without needing a longer baseline to take time averages. Had we been following only a few bodies, this would not have been the case.

### 2020-10-29 main.tex
More edits

The dynamical effects of secular forcing by the giant planet, along with  the effects of viscous stirring and gas drag on the planetesimals, are 
built into the initial conditions. This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a 
function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. Although {\sc ChaNGa} does not account for the effects of 
gas drag on the planetesimals, the viscous stirring timescale is long compared to our integration time and should not cause the velocity 
distribution to significantly evolve. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. The arguments of perihelion 
$\omega$, longitude of ascending nodes $\Omega$ and the mean anomalies $M$ of the bodies are drawn uniformly $\in [0, 2 \pi)$.

@@

All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{1999ssd..book.....M})
\begin{equation}\label{eq:lib_time}
	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| 2p + q \right|}},
\end{equation}

\noindent for small-amplitude librations. For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances. 
For this reason, we allow each simulation to run for 2,000 years before we begin recording any collision statistics.

>>>>

The dynamical effects of secular forcing by the giant planet, along with  the effects of viscous stirring and gas drag on the planetesimals, are 
built into the initial conditions. \textbf{Although we do not model the effects of gas drag on the planetesimals, we construct the initial conditions such that these two effects are in balance. The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without modeling damping from gas.}. This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a 
function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. Although {\sc ChaNGa} does not account for the effects of 
gas drag on the planetesimals, the viscous stirring timescale is long compared to our integration time and should not cause the velocity 
distribution to significantly evolve. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. The arguments of perihelion 
$\omega$, longitude of ascending nodes $\Omega$ and the mean anomalies $M$ of the bodies are drawn uniformly $\in [0, 2 \pi)$.

@@

All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{1999ssd..book.....M})
\begin{equation}\label{eq:lib_time}
	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| -q \right|}},
\end{equation}

\noindent for small-amplitude librations. For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances. 
For this reason, we allow each simulation to run for 2,000 years before we begin recording any collision statistics. \textbf{Although the integration time we use
is only a tiny fraction of the Myr timescales that a typical protoplanetary disk lives for (citation?), 5,000 years is sufficient to allow all of the relevant dynamics here.
As discussed above in section \ref{sec:ics}, the initial conditions are constructed so that relevant effects with longer timescales (such as gravitational stirring, gas drag on planetesimals and secular forcing) are already in equilibrium.}
